### 2020-05-27 manuscript/manuscript-climate-policy.tex
Update README.md, add Dataverse DOI

\documentclass[a4paper,12pt]{article}
\usepackage{titling}
\usepackage{lscape}
\usepackage{amssymb, amsmath, amssymb}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage[stable]{footmisc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=.9]{inconsolata}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{float}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{dcolumn}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[english]{babel}
\usepackage[authoryear]{natbib}
\usepackage{babelbib}
\usepackage{bibentry}
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=10000
\clubpenalty=10000
\setcitestyle{aysep={}} 
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
\makeatother
\usepackage[hyphens]{url}
\usepackage[hidelinks]{hyperref}

@@

\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Frans Berkhout, Daniel D'Amico, Guilherme Fasolin, Manoel Galdino, Malte Hendricks, Stephen Herzog, Christian H\"{u}bner, Karina Marzano, Davi Moreira, Emily Skarbek, Paula Vedovelli, and the participants at the FGV IR Seminar for their valuable comments. Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana, and Larissa Santos for their excellent research assistance. This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Getulio Vargas (Protocol 83/2018). We acknowledge financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS) and declare there are no conflicts of interest. The data, code, and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}}

\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, \href{mailto:danilo_freire@brown.edu}{\texttt{danilo\_freire@brown.edu}}, \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}, \href{http://twitter.com/danilofreire}{\texttt{http://twitter.com/danilofreire}}, Voice: +1 (401) 584-2494. Corresponding author.}
\and Umberto Mignozzetti\thanks{School of International Relations, Funda\c{c}\~{a}o Getulio Vargas, S\~{a}o Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, \href{mailto:umberto.mignozzetti@fgv.br}{\texttt{umberto.mignozzetti@fgv.br}}, \href{http://umbertomig.com}{\texttt{http://umbertomig.com}}, \href{http://twitter.com/umbertomig}{\texttt{http://twitter.com/umbertomig}}.}
\and David Skarbek\thanks{The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}, \href{http://twitter.com/davidskarbek}{\texttt{http://twitter.com/davidskarbek}}.}}

\date{November 20, 2019}

@@

\begin{abstract}
\onehalfspacing
\noindent 
Which institutional features do Latin American elites favor for local climate change policies? Climate change mitigation requires active local level implementation, but it remains unclear which institutional arrangements maximize the support for environmental rules. In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs drawn from a pool of 5,500 possible local climate governance arrangements. We find that Latin American elites prefer international organizations to formulate climate policies, support imposing increasing fines on violators, and favor renewing agreements every five years. We also find that elites support both international institutions and local courts to mediate conflicts, but they distrust non-governmental organizations and reject informal norms as a means of conflict resolution. Our results identify possible challenges in crafting local climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements.

@@

These concerns have motivated a growing debate about which institutional characteristics lead to successful climate agreements \citep[e.g.,][]{bechtel2013mass, bechtel2017interests, keohane2011regime, mitchell2006problem, ostrom2014polycentric}. Climate treaties are incomplete contracts, in which members purposefully design flexible provisions that take domestic circumstances into account \citep[607]{brauninger2000making}. For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve \citep{winning2019nationally}. This decentralization increases the importance of local stakeholders in climate negotiations, and studies have shown that the behavior of elite groups -- specially that of advocacy coalitions and political networks -- largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}. Elites can advance or constrain climate agreements using `societal steering' strategies such as capacity building and rule setting, thus acting as \textit{de facto} veto players in local environmental policies \citep{andonova2009transnational, bulkeley2014transnational}.

Although research on public opinion and climate agreements has increased significantly in the last years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature. This is a significant omission considering that recent work has stressed the impact of elite coalitions in areas such as global finance and international banking regulation \citep[e.g,][]{chalmers2017banks, pagliari2014leveraged}. Elites in developing countries are specially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}. It is unclear which local climate strategies face lower internal resistance from these groups, or whether their environmental preferences are fundamentally different from those of their developed countries counterparts \citep[28]{aklin2013understanding}.

We help remedy this gap by assessing which local climate mitigation initiatives Latin American elites are willing to support. In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople and members of non-governmental organizations -- to select their preferred components for local climate mitigation among 7 repetitions of binary choices. We vary the agreements across six dimensions commonly debated in the climate change and institutional design literatures: rule-making capabilities \citep{dubash2013developments, massey2014climate}; conflict resolution mechanisms \citep{huntjens2012institutional, ostrom2014polycentric}; enforcement methods \citep{barrett2008climate}; punishment for repeated violators \citep{ostrom1990governing}; cost sharing \citep{bansak2017europeans,bechtel2013mass}; and agreement duration \citep{copelovitch2014design, marcoux2009institutional}. Variations in any of those features can substantially change the outcomes of climate institutions \citep{bodin2017collaborative, ostrom2014polycentric}.

We find that interviewees prefer international organizations to design local climate policies and are favorable to imposing increasing fines on violators and renegotiating agreements every five years. Survey participants also want both international institutions and local courts to mediate conflicts, but they are skeptical about non-governmental organizations and consistently reject informal norms as an instrument to solve disputes. The results lend support to theories that define climate governance as a `regime complex' \citep{colgan2012punctuated, keohane2011regime}, that is, `an array of partially overlapping and non-hierarchical institutions govern a particular issue area' \citep[279]{raustiala2004regime}. Moreover, following the spirit of the Paris Accords, the regime complex framework stresses the role of elite perceptions on the relationship between local and global climate mitigation efforts. Our findings suggest that Latin American elites embrace the complexity of climate policy and believe mitigation policies should incorporate several layers of governance simultaneously.

@@

Second, we contribute to classical theories on international regimes. \citet{abbott2000hard} introduce the idea of hard versus soft international law to explain why actors pursue a variety of legal agreements to foster their interests in the international realm. \citet{mildenberger2017beliefs} and \citet{rosendorff2001optimal} posit that when compliance is hard to observe, incomplete contracts are superior as they avoid unnecessary punishments and improve long-run cooperation stability. \citet{keohane2011regime}, in turn, argue that non-hierarchical international rulings help states to avoid gridlocks by reducing contracting costs and embracing `problem diversity', in which each particular climate problem requires a specific solution. Our results corroborate that flexible regime designs are decisive to foster international cooperation.

Finally, we also present novel information on Latin American elite behavior regarding climate institutions. Our findings indicate that elites in Latin America favor agreements that do not fit into the broad categories of `centralization' or `polycentrism'; instead, they prefer a combination of the two. The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but respondents also believe that both international and subnational institutions should play a role in local climate policy design. The data provide new insights on how Latin American policy-makers can form domestic coalitions and which climate mitigation agreement faces lower resistance from potential veto players \citep{beiser2019commitment, hovi2019club}.

@@

We use conjoint experiments to estimate the effect of institutional features on climate mitigation agreements. A conjoint experiment is a statistical technique that allows individuals to express their preferences on multiple attributes of a single topic \citep{bansak2016economic, hainmueller2014causal}. Individuals are presented with two hypothetical scenarios, each containing a randomly assigned series of characteristics a researcher wants to evaluate. The individual selects one of them. As the attributes are randomized, we can estimate how individuals value each of the conjoined elements relative to their alternatives.\footnote{We note, however, that our conjoint experiments do not allow us to infer the average level of attribute support in the sample. Since our design relies on forced choices, estimates should always be interpreted in comparison to the other attributes in the alternative agreement bundle.}

@@

We use an original dataset compiled specifically for this study. From October 1 to December 5, 2018, we ran an elite survey with respondents from Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama and Peru. We started by gathering information on potential interviewees. For each country, we collected the profiles of 100 members of the Executive, 100 members of the Legislative, 150 academics in the energy sector and 150 members of the civil society. We then sampled these profiles until we achieved a minimum of 10\% of responses within each group. We ran our survey both online and by telephone, collecting information on the climate change agreements and other related questions in a non-intrusive manner \citep{loewen2010help}. We had two teams of enumerators, one based in S\~{a}o Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers. Please refer to the Supplementary Material for more information about the sampling process and descriptive statistics.

The hypothetical climate change agreements include six attributes: 1) which organizations defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated. Table~\ref{tab:categories} describes the values we included in each treaty attribute.\footnote{A discussion on the theoretical underpinnings of our choice of attributes is available in the Supplementary Material.}

@@

@@

@@

\begin{figure}[h]
	\centering
	\includegraphics[height=12cm]{MM_all.pdf}
	\caption{\textbf{Relative preferences for institutional attributes in climate change agreements in 10 Latin American countries (pooled data, marginal means)}}
	\label{fig:pooled}
\end{figure}

Respondents prefer international organizations to establish local climate mitigation rules (54\%, SE = 1.2), but they also hold relatively favorable views of local communities (51.6\%, SE = 1.25). We note that Latin American elites support multiple governance levels simultaneously, which suggests that they are willing to include separate political spheres into a single climate policy design. Local governments (49.8\%, SE = 1.2) and federal governments (48.6\%, SE = 1.3) are slightly preferred over NGOs, yet the difference between them is not statistically significant. Non-governmental organizations are the least preferred option for local climate change rule-making with 45.5\% (SE = 1.3).

@@

Regarding local agreements' renegotiations, respondents are interested in a balance between stability and flexibility. Interviewees reject agreements that either cannot be modified or that last for 50 years. Their preference lies in agreements that can be renegotiated every five years (59\%, SE = 1.2). This is consistent with a concern that agreements should be durable enough to provide long-term incentives to the parties, yet remain adaptable to unforeseen demands.

@@

We observe higher variance in the responses related to the frequency of treaty renegotiations and in those concerning the methods of conflict resolution. We believe that both items vary considerably because elites are concern about the region's long history of political and economic volatility. Elites might be divided over which strategy is best to achieve climate mitigation goals. On the one hand, some respondents prefer long-term agreements to induce stronger commitment to fight climate change. On the other hand, different groups of respondents may expect continuing instability in Latin America and therefore prefer to make agreements more flexible to cope with future chances. Moreover, Latin America's historically low levels of trust in public institutions may have spurred elites to have divergent opinions about which institution should be responsible for punishing non-compliers.

@@

\begin{figure}[hbpt]
	\centering
	\includegraphics[width=\linewidth, height=20cm]{MM_country.pdf}
	\caption{\textbf{Relative preferences for institutional attributes in climate change agreements by country (marginal means)}}
	\label{fig:countries}
\end{figure}

However, some of the regional preferences are a by-product of sample aggregation. Latin American elites do not have a consensus on which organizations should provide the rules. For example, elites in Costa Rica prefer local to global rule-making; in Mexico, they prefer global and dislike local, similar to Peru, Argentina and Brazil; in Colombia, elites favor global and local rule-making simultaneously; and in Bolivia, respondents prefer local organizations to design local climate rules. This is an important point and might have far-reaching consequences for environmental policy design. The lack of coordination on rule-making responsibilities can give rise to decision cycles, lowering the chance that a single, favourite climate change solution emerges. Nevertheless, these dissensions might be resolved by decentralization, boosting the idea that flexible regime complexes, such as polycentric governance schemes, might provide a solution to gridlocks.

@@

Differences emerge in two of the six attributes. Academics and members of the civil society are skeptical about the role of federal government in local climate policy-making, while members of the executive and legislative --- part of the government themselves --- have a more positive view of national institutions. The differences, however, are not large. Second, members of the legislative prefer rich countries to bear the larger part of agreement costs (58.4\%, SE = 3.5). This provides evidence for the idea of historical responsibility for climate protection, an argument which developing countries have recently brought to climate negotiations \citep{muller2009differentiating, friman2015agreement}.

@@

Our results have several theoretical and practical implications. The findings we present here suggest there is considerable scope for new studies on local challenges to global governance, specially in underrepresented regions. Our analysis can be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to know what explains the mismatch between groups \citep{luna2005political}. Moreover, future work may address whether elites in other regions also understand climate policy as a regime complex, in which different actors play a constructive yet decentralized role in policy-making.

@@

@@

For supplementary material for this article, please visit \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.

\bibliographystyle{apalike}
\bibliography{references.bib}

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{titling}
\usepackage{lscape}
\usepackage{amssymb, amsmath, amssymb}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage[stable]{footmisc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=.9]{inconsolata}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{float}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{dcolumn}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[english]{babel}
\usepackage{natbib}
\usepackage{babelbib}
\usepackage{bibentry}
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=10000
\clubpenalty=10000
\setcitestyle{aysep={}} 
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
\makeatother
\usepackage[hyphens]{url}
\usepackage[hidelinks]{hyperref}

@@

\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Frans Berkhout, Daniel D'Amico, Guilherme Fasolin, Manoel Galdino, Malte Hendricks, Stephen Herzog, Christian H\"{u}bner, Karina Marzano, Davi Moreira, Emily Skarbek, Paula Vedovelli, and the participants at the FGV IR Seminar for their valuable comments. Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana, and Larissa Santos for their excellent research assistance. We would also like to thank two anonymous reviewers for their helpful comments and suggestions. This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Getulio Vargas (Protocol 83/2018). We acknowledge financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS) and declare there are no conflicts of interest. The data, code, and any additional materials required to replicate all analyses in this article are available at the Journal of Experimental Political Science Dataverse within the Harvard Dataverse Network, at: \href{https://doi.org/10.7910/DVN/VTA5OA}{\texttt{doi:10.7910/DVN/VTA5OA}}.}}

\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, \href{mailto:danilo_freire@brown.edu}{\texttt{danilo\_freire@brown.edu}}, \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}. Corresponding author.}
\and Umberto Mignozzetti\thanks{School of International Relations, Funda\c{c}\~{a}o Getulio Vargas, S\~{a}o Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, \href{mailto:umberto.mignozzetti@fgv.br}{\texttt{umberto.mignozzetti@fgv.br}}, \href{http://umbertomig.com}{\texttt{http://umbertomig.com}}, \href{http://twitter.com/umbertomig}{\texttt{http://twitter.com/umbertomig}}.}
\and David Skarbek\thanks{The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}, \href{http://twitter.com/davidskarbek}{\texttt{http://twitter.com/davidskarbek}}.}}

\date{\today}

@@

\begin{abstract}
\singlespacing
\noindent 
Which institutional features do Latin American elites favor for local climate change policies? Climate change mitigation requires active local level implementation, but it remains unclear which institutional arrangements maximize support for environmental rules. In this paper, we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate institutional designs drawn from a pool of 5,500 possible local climate governance arrangements. We find that Latin American elites prefer international organizations to formulate climate policies, support imposing increasing fines on violators, and favor renewing agreements every five years. We also find that elites support both international institutions and local courts to mediate conflicts, but they distrust non-governmental organizations and reject informal norms as a means of conflict resolution. Our results identify possible challenges in crafting local climate mitigation policies and offer new insights about how to integrate local and international levels in environmental agreements.

@@

These concerns have motivated a growing debate about which institutional characteristics lead to successful climate agreements \citep[e.g.,][]{bechtel2013mass, bechtel2017interests, keohane2011regime, mitchell2006problem, ostrom2014polycentric}. Climate treaties are incomplete contracts, in which members purposefully design flexible provisions that take domestic circumstances into account \citep[607]{brauninger2000making}. For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve \citep{winning2019nationally}. This decentralization increases the importance of local stakeholders in climate negotiations, and studies have shown that the behavior of elite groups -- especially that of advocacy coalitions and political networks -- largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}. Elites can advance or constrain climate agreements using `societal steering' strategies such as capacity building and rule setting, thus acting as \textit{de facto} veto players in local environmental policies \citep{andonova2009transnational, bulkeley2014transnational}.

Although research on public opinion and climate agreements has increased significantly in recent years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature. This is a significant omission considering that recent work has stressed the impact of elite coalitions in areas such as global finance and international banking regulation \citep[e.g,][]{chalmers2017banks, pagliari2014leveraged}. Elites in developing countries are especially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}. It is unclear which local climate strategies face lower internal resistance from these groups, or whether their environmental preferences are fundamentally different from those of their developed countries counterparts \citep[28]{aklin2013understanding}.

We remedy this gap by assessing which local climate mitigation initiatives Latin American elites are willing to support. In our survey experiment, we asked 654 respondents -- academics, members of the executive power, legislators, businesspeople, and members of non-governmental organizations -- to select their preferred components for local climate mitigation among seven repetitions of binary choices. We vary the agreements across six dimensions commonly debated in the climate change and institutional design literatures: rule-making capabilities \citep{dubash2013developments, massey2014climate}; conflict resolution mechanisms \citep{huntjens2012institutional, ostrom2014polycentric}; enforcement methods \citep{barrett2008climate}; punishment for repeated violators \citep{ostrom1990governing}; cost sharing \citep{bansak2017europeans,bechtel2013mass}; and agreement duration \citep{copelovitch2014design, marcoux2009institutional}. Variations in any of those features can substantially change the outcomes of climate institutions \citep{bodin2017collaborative, ostrom2014polycentric}.\footnote{As we discuss below, we take a parsimonious approach in regards to the number of dimensions included in the experiment. In the Supplemental Material, we show that these components are commonly debated by Latin American elites.}

We find that interviewees prefer international organizations to design local climate policies and are favorable to imposing increasing fines on violators and renegotiating agreements every five years. Survey participants also want both international institutions and local courts to mediate conflicts, but they are skeptical about non-governmental organizations and consistently reject informal norms as an instrument to solve disputes. The results lend support to theories that define climate governance as a `regime complex' \citep{colgan2012punctuated, keohane2011regime}, that is, `an array of partially overlapping and non-hierarchical institutions [that] govern a particular issue area' \citep[279]{raustiala2004regime}. Moreover, following the spirit of the Paris Accords, the regime complex framework stresses the role of elite perceptions on the relationship between local and global climate mitigation efforts. Our findings suggest that Latin American elites embrace the complexity of climate policy and believe mitigation policies should incorporate several layers of governance simultaneously.

@@

Second, we contribute to classical theories on international regimes. \citet{abbott2000hard} introduce the idea of hard versus soft international law to explain why actors pursue a variety of legal agreements to foster their interests in the international realm. \citet{mildenberger2017beliefs} and \citet{rosendorff2001optimal} posit that when compliance is hard to observe, incomplete contracts are superior as they avoid unnecessary punishments and improve long-run cooperation stability. \citet{keohane2011regime}, in turn, argue that non-hierarchical international rulings help states avoid gridlocks by reducing contracting costs and embracing `problem diversity', in which each particular climate problem requires a specific solution. Our results suggest that flexible regime designs are decisive to foster international cooperation.

Finally, we also present novel information on Latin American elite behavior regarding climate institutions. Our findings indicate that elites in Latin America favor agreements that do not fit into the broad categories of `centralization' or `polycentrism'; instead, they prefer a combination of the two. The results are consistent with the Latin American tradition of heavier reliance on the state than on self-governed solutions, but respondents also believe that both international and subnational institutions should play a role in local climate policy design. The data offer new insights on how Latin American policy-makers can form domestic coalitions and provides a first exploration of how regional elites understand the nature of climate change mitigation efforts.

@@

We use conjoint experiments to estimate the effect of institutional features on climate mitigation agreements. A conjoint experiment is a statistical technique that allows individuals to express their preferences on multiple attributes of a single topic \citep{bansak2016economic, hainmueller2014causal}. Individuals are presented with two hypothetical scenarios, each containing a randomly assigned series of characteristics a researcher wants to evaluate. The individual selects one of them. As the attributes are randomized, we can estimate how individuals value each of the conjoined elements relative to their alternatives.\footnote{We note, however, that our research design only allows us to infer the average level of attribute support within the context of the conjoint experiment. Since our design relies on forced choices, respondents are required to choose 50\% of the agreement bundles presented to them. In this respect, the findings we observe here may be different from what would see should respondents vote yes or no on a single package, without another agreement bundle for comparison. We elaborate on this issue in the discussion section and in the Supplementary Material.}

@@

We use an original dataset compiled specifically for this study. From October 1 to December 5, 2018, we ran an elite survey with respondents from Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama and Peru. We started by gathering information on potential interviewees. For each country, we collected the profiles of 100 members of the executive branch, 100 members of the legislative branch, 150 academics in the energy sector and 150 members of the civil society. We then sampled these profiles until we achieved a minimum of 10\% of responses within each group. We ran our survey both online and by telephone, collecting information on the climate change agreements and other related questions in a non-intrusive manner \citep{loewen2010help}. We had two teams of enumerators, one based in S\~{a}o Paulo and another based in Rio de Janeiro, Brazil, composed of Portuguese and Spanish native speakers. Please refer to the Supplementary Material for more information about the sampling process and descriptive statistics. \\

@@

The hypothetical climate change agreements include six attributes: 1) which organizations define the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated. Table~\ref{tab:categories} describes the values we included in each treaty attribute.\footnote{A discussion on the theoretical underpinnings of our choice of attributes is available in the Supplementary Material.}

@@

In designing the experiment, we attempted to strike a balance between realism and parsimony. Local implementation of climate agreements may vary among a wide set of dimensions, but including too many attributes in the conjoint design would significantly increase cognitive load and induce respondent fatigue \citep{pullman1999comparison}. Subjects also use decision heuristics when the number of conjoint attributes is high, such as focusing on the dimensions they care the most or on the ones they see first. These issues lead to uninformative experimental results \citep{lines2004information}. In this respect, we decided to restrict the total of categories at the expense of some loss of external validity. However, if individuals found our choice of attributes too unrealistic, we would expect a high number of non-responses in the survey. Our data show that this was not the case. Conditional on having answered the first task, completion rates for the last task were around 90\% across countries and elite types, which suggests that respondents did engage in the experiment and that the offered options made intuitive sense to them.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[height=12cm]{MM_all.pdf}
	\caption{\textbf{Relative preferences for institutional attributes in climate change agreements in 10 Latin American countries (pooled data, marginal means)}}
	\label{fig:pooled}
\end{figure}

Respondents prefer international organizations to establish local climate mitigation rules (54\%, SE = 1.2), but they also hold relatively favorable views of local communities (51.6\%, SE = 1.25). We note that Latin American elites support multiple governance levels simultaneously, which suggests that they are willing to include separate political spheres into a single climate policy design. Local governments (49.8\%, SE = 1.2) and federal governments (48.6\%, SE = 1.3) are slightly preferred over NGOs, yet the difference between the former two is not statistically significant. Non-governmental organizations are the least preferred option for local climate change rule-making with 45.5\% (SE = 1.3).

@@

When we analyze local agreements' renegotiations, respondents are interested in a balance between stability and flexibility. Interviewees reject agreements that either cannot be modified or that last for 50 years. Their preference lies in agreements that can be renegotiated every five years (59\%, SE = 1.2). This is consistent with a concern that agreements should be durable enough to provide long-term incentives to the parties, yet remain adaptable to unforeseen demands.

@@

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth, height=20cm]{MM_country.pdf}
	\caption{\textbf{Relative preferences for institutional attributes in climate change agreements by country (marginal means)}}
	\label{fig:countries}
\end{figure}

However, some of the regional preferences are a by-product of sample aggregation. Latin American elites do not have a consensus on which organizations should provide the rules. For example, elites in Costa Rica prefer local to global rule-making; in Mexico, they prefer global and dislike local, similar to Peru, Argentina and Brazil; in Colombia, elites favor global and local rule-making simultaneously; and in Bolivia, respondents prefer local organizations to design local climate rules. This is an important point and might have far-reaching consequences for environmental policy design. The lack of coordination on rule-making responsibilities can give rise to decision cycles, lowering the chance that a single, favorite climate change solution emerges. Nevertheless, these dissensions might be resolved by decentralization, boosting the idea that flexible regime complexes, such as polycentric governance schemes, might provide a solution to gridlocks.

@@

Differences emerge in two of the six attributes. Academics and members of the civil society are skeptical about the role of federal government in local climate policy-making, while members of the executive and legislative branches --- part of the government themselves --- have a more positive view of national institutions. The differences, however, are not large. Second, members of the legislative branch prefer rich countries to bear the larger part of agreement costs (58.4\%, SE = 3.5). This provides evidence for the idea of historical responsibility for climate protection, an argument which developing countries have recently brought to climate negotiations \citep{muller2009differentiating, friman2015agreement}.

@@

@@

We believe our findings can be extended in many ways. The research design we employ here provides only a first step towards understanding the behavior of local elites and their preferences regarding climate change policies. Our use of forced choices implies that we could not measure the overall level of attribute support in the elite population, when respondents can choose any agreement they prefer without constraints. Moreover, further research could better adjudicate between rules associated with the global treaty negotiations themselves and those concerning domestic politics. For instance, future studies may analyze how each country's specific legal framework imposes constraints we did not include in our experiment, and thus provide fine-grained information about local attitudes towards climate agreements. Moreover, scholars may employ other types of research designs, such as vignette experiments or qualitative interviews, to assess the robustness of our results. Lastly, our analysis can also be extended to examine if the Latin American public has the same opinion on multilevel arrangements as do the elites; and if not, it would be important to know what explains the mismatch between groups \citep{luna2005political}.

@@

For supplementary material for this article, please visit \url{http://github.com/danilofreire/climate-governance}.

\nocite{freire2020replication}
\bibliographystyle{apalike}
\bibliography{references.bib}
